Title here

### 2016-09-14 portfolio/text/ms.Rmd
Keep developing methods

- overview
- describe predictors
- We adjusted for inflation by setting all revenues in 2009 USD 
based on data from TODO.
- note the filtering and referred to the supplement

## Predictors

Our models focused on the predictor species diversity, 
while controlling for effort. We calculated effective species diversity for
permit holder $i$ and year $t$ as the inverse of 
Simpson's diversity index $\lambda$ [@simpson1949]
weighted by revenue $R$ (herein 'species diversity'):

@@

The term $\log(R_{i,t-1}$) is treated as an offset term:
it is added on the right side of the equation
to essentially model percent change in revenue,
i.e., $\log(R_{i,t}) - \log(R_{i,t-1}) = \log(R_{i,t}/R_{i,t-1})$.
While this approach required filtering the data 
to remove person-year combinations without a subsequent year of revenue,
it has a number of advantages: 
it eliminates having to deal with the nonstationary 
timeseries and eliminates having to 
estimate thousands of people-specific intercepts.

>>>>

- overview

## Data

We obtained landings and revenue data for 
all permit holders in Alaska 
from `r range_yrs[1]` to `r range_yrs[2]`
from the Alaskan Commercial Fisheries Entry Commission (CFEC).
These data represent a total of 
nearly `r round(ndat$initial_tot_rev/1e9)` billion 2009 USD
and a combined `r round(ndat$initial/1e6,1)` million rows of data.
We adjusted for inflation by setting all revenues in 2009 USD 
based on data from TODO.
We implemented a number of filtering steps 
to focus on individuals actively engaged in commercial fishing
(Supporting Information). 
In particular, we removed permit holders whose median revenue
was less than $10,000 2009 USD.

Our models focused on the predictor species diversity, 
while controlling for effort. 
We calculated effective species diversity for
permit holder $i$ and year $t$ as the inverse of 
Simpson's diversity index $\lambda$ [@simpson1949]
weighted by revenue $R$ ('species diversity'):

@@

The term $\log(R_{i,t-1}$) is treated as an offset term:
it is added on the right side of the equation
to essentially model percent change in revenue,
i.e., $\log(R_{i,t}) - \log(R_{i,t-1}) = \log(R_{i,t}/R_{i,t-1})$.
While this approach required filtering the data 
to remove person-year combinations without a subsequent year of revenue,
it has a number of advantages: 
it eliminates having to deal with the non-stationary 
time series and eliminates having to 
estimate thousands of people-specific intercepts.
